Measurement and Probability in Fuzzy Quantum Theories

### 2017-05-04 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$ and a function~$\tau:\events'\rightarrow2^{\Omega}$
such that:
\begin{itemize}
\item If $\mu:\events'\rightarrow\left[0,1\right]$ is a quantum real-valued
probability measure, then there is a classical real-valued probability
measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item If $\bar{\mu}:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
probability measure, then there is a classical interval-valued probability
measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
$\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$
\end{itemize}
\end{thm}

\begin{proof}Again, it is sufficient to prove the interval-valued
case. Since $\events'$ is a set of mutually orthogonal projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}

@@

Since there is a correspondence between classical probability measures
and quantum ones on a commuting sub-event space, we can use the quantum
language to describe the classical world given a commuting sub-event
space.

>>>>

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{itemize}
\item If $\mu:\events'\rightarrow\left[0,1\right]$ is a quantum real-valued
probability measure, then there is a classical real-valued probability
measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item If $\bar{\mu}:\events'\rightarrow\mathscr{I}$ is a quantum interval-valued
probability measure, then there is a classical interval-valued probability
measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
$\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\end{itemize}
\end{thm}

\begin{proof}Again, it is sufficient to prove the interval-valued
case. Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}

@@

Since there is a correspondence between classical probability measures
and quantum ones on a commuting sub-event space, we can use the quantum
language to describe the classical world given an orthonormal basis.

\begin{definition}Given a Hilbert space~$\Hilb$, an orthonormal
basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$, and a classical
real-valued probability measures~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
on the sample space~$\Omega$, the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}$
is called classical with respect to $\Omega$.\end{definition}

Then, we can rephrase theorem~\ref{thm:Shapley}, in the language
of quantum IVPM with an orthonormal basis.

\begin{cor}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
if $\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}

\begin{proof}Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
By theorem~\ref{thm:sub-event-space}, we can find a bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
and a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Since $\tau$ is a bijection, $\bar{\mu}'$
is convex. By theorem~\ref{thm:Shapley}, there is a. classical probability
measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$ such that
\begin{eqnarray*}
 &  & \pmeas\in\mathrm{core}\left(\bar{\mu}'\right)\\
 & \Rightarrow & \pmeas\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)\textrm{ for all }P\in\widehat{\events}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}
\end{eqnarray*}
Then, it is easy to verify that the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
